---
title: "replication_main_results"
author: "Meera Duggal"
date: "5/4/2022"
output: pdf_document 
---

```{r}
library(haven)
library(RStata)
library(tidyverse)
library(lemon)
library(knitr)
library(kableExtra)
library(magrittr)
library(lmtest)
library(sandwich)
knit_print.data.frame <- lemon_print

# read in the data
household_df <- read_dta('PisoFirme_AEJPol-20070024_household.dta')
individual_df <- read_dta('PisoFirme_AEJPol-20070024_individual.dta')
```

### Imputing Missing Values 

Imputing the values for just the X values 
```{r}
household_X <- household_df
household_X[is.na(household_X)] <- 0

individual_X <- individual_df
individual_X[is.na(individual_X)] <- 0

individual_Y <- individual_df
household_Y <- household_df

```

## Code for Table 4 !!!! 
Motivation here: Different dummy variables where created depending on if they had cement floors, kitchen has cement floors, dining room had cement floors, bathroom has cement floos, and if household members sleep in rooms w cement floors. 

Regressions of Cement Floor Coverage Measures on Program Dummy

They define three different models for all tables: model 1, 2, 3 

### Code for First 2 columns in Table 4 
Control group: means and standard deviation 
model 1: this has no controls 
```{r}
library(lmtest)
library(sandwich)

dependent_vars <- cbind(household_Y$S_shcementfloor, household_Y$S_cementfloorkit, household_Y$S_cementfloordin, household_Y$S_cementfloorbat, household_Y$S_cementfloorbed)

ctrl_grp_mean <- c()
stds <- c()
coefs <- c()
cl_se <- c()

for(i in 1:5){
  #intercept 
  model1 <- lm(dependent_vars[,i] ~ household_X$dpisofirme)
  
  #first column
  ctrl_grp_mean <- append(ctrl_grp_mean, summary(model1)$coefficients[1,1])
  
  #second value in first column 
  stds[i] <- summary(model1)$coefficients[1,2] * sqrt(nrow(household_X))
  

  #clustered standard error 
  #value in the brackets 
  cl_se[i] <-coeftest(model1, vcov=vcovCL, cluster= household_X$idcluster)[2,2]

  #coefficient for dpisofirme 
  coefs[i] <-  model1$coefficients[2]
  
  
}


coef_over_mean <- 100*(coefs / ctrl_grp_mean)


```

### Code for 3rd columns in Table 4 

HHmodel_2 $HH_demog1 dmiss_HH_demog1* $HH_demog2 dmiss_HH_demog2* $HH_health dmiss_HH_health*;

HH_demog1  S_HHpeople S_headage S_spouseage S_headeduc S_spouseeduc;
HH_demog2 S_dem1 S_dem2 S_dem3 S_dem4 S_dem5 S_dem6 S_dem7 S_dem8;

HH_health  S_waterland S_waterhouse S_electricity S_hasanimals S_animalsinside S_garbage S_washhands;

model 2: age, demogrpahic, health-habits controls 
```{r}

coefs <- c()
cl_se <- c()

for(i in 1:5){
  #intercept 
  model1 <- lm(dependent_vars[,i] ~ household_X$dpisofirme + household_X$S_HHpeople + household_X$S_headage + 
                 household_X$S_spouseage + household_X$S_headeduc + household_X$S_spouseeduc + household_X$S_dem1 + household_X$S_dem2 + 
                 household_X$S_dem3 + household_X$S_dem4 + household_X$S_dem5 + household_X$S_dem6 + household_X$S_dem7 + household_X$S_dem8 + 
                 household_X$S_waterland + household_X$S_waterhouse + household_X$S_electricity + household_X$S_hasanimals + 
                 household_X$S_animalsinside + household_X$S_garbage + household_X$S_washhands)


  #clustered standard error 
  #value in the brackets 
  cl_se[i] <-coeftest(model1, vcov=vcovCL, cluster= household_X$idcluster)[2,2]

  #coefficient for dpisofirme 
  coefs[i] <-  model1$coefficients[2]
  
  
}


coef_over_mean <- 100*(coefs / ctrl_grp_mean)


```

### Code for 4th columns in Table 4 

HHmodel_3 $HH_demog1 dmiss_HH_demog1* $HH_demog2 dmiss_HH_demog2* 
$HH_health dmiss_HH_health* $HH_social dmiss_S_cash*;

HH_demog1  S_HHpeople S_headage S_spouseage S_headeduc S_spouseeduc;
HH_demog2 S_dem1 S_dem2 S_dem3 S_dem4 S_dem5 S_dem6 S_dem7 S_dem8;

HH_health  S_waterland S_waterhouse S_electricity S_hasanimals S_animalsinside S_garbage S_washhands;

HH_social  S_cashtransfers S_milkprogram S_foodprogram S_seguropopular

model 3: age, demographic, health- habits, and public social programs controls

```{r}

coefs <- c()
cl_se <- c()

for(i in 1:5){
  #intercept 
  model1 <- lm(dependent_vars[,i] ~ household_X$dpisofirme + household_X$S_HHpeople + household_X$S_headage + 
                 household_X$S_spouseage + household_X$S_headeduc + household_X$S_spouseeduc + household_X$S_dem1 + household_X$S_dem2 + 
                 household_X$S_dem3 + household_X$S_dem4 + household_X$S_dem5 + household_X$S_dem6 + household_X$S_dem7 + household_X$S_dem8 + 
                 household_X$S_waterland + household_X$S_waterhouse + household_X$S_electricity + household_X$S_hasanimals + 
                 household_X$S_animalsinside + household_X$S_garbage + household_X$S_washhands + household_X$S_cashtransfers +
                 household_X$S_milkprogram + household_X$S_foodprogram + household_X$S_seguropopular
               , data = household_X)


  #clustered standard error 
  #value in the brackets 
  cl_se[i] <-coeftest(model1, vcov=vcovCL, cluster= household_X$idcluster)[2,2]

  #coefficient for dpisofirme 
  coefs[i] <-  model1$coefficients[2]
  
  
}


coef_over_mean <- 100*(coefs / ctrl_grp_mean)


```
#### TABLE 5


S_parcount S_diarrhea S_anemia S_mccdts S_pbdypct S_haz S_whz;
## MODEL 1
```{r}
dependent_vars <- cbind(individual_Y$S_parcount, individual_Y$S_diarrhea, individual_Y$S_anemia, individual_Y$S_mccdts, individual_Y$S_pbdypct, individual_Y$S_haz, individual_Y$S_whz)

ctrl_grp_mean <- c()
stds <- c()
coefs <- c()
cl_se <- c()

for(i in 1:7){
  #intercept 
  model1 <- lm(dependent_vars[,i] ~ individual_X$dpisofirme)
  
  #first column
  ctrl_grp_mean <- append(ctrl_grp_mean, summary(model1)$coefficients[1,1])
  
  #second value in first column 
  stds[i] <- summary(model1)$coefficients[1,2] * sqrt(nrow(individual_X))
  

  #clustered standard error 
  #value in the brackets 
  cl_se[i] <-coeftest(model1, vcov=vcovCL, cluster= individual_X$idcluster)[2,2]

  #coefficient for dpisofirme 
  coefs[i] <-  model1$coefficients[2]
  
  
}

coef_over_mean <- 100*(coefs / ctrl_grp_mean)


```


## model 2: age, demogrpahic, health-habits controls 
gl INmodel_2 $CH_demog dmiss_CH_demog* dtriage* $HH_health dmiss_HH_health*;
```{r}

coefs <- c()
cl_se <- c()

for(i in 1:7){
  #intercept 
  model1 <- lm(dependent_vars[,i] ~ individual_X$dpisofirme + 
                 individual_X$S_HHpeople + individual_X$S_rooms + 
                 individual_X$S_age + individual_X$S_gender + 
                 individual_X$S_childma + individual_X$S_childmaage + 
                 individual_X$S_childmaeduc + 
                 individual_X$S_childpa + individual_X$S_childpaage + 
                 individual_X$S_childpaeduc + individual_X$S_waterland + individual_X$S_waterhouse + individual_X$S_electricity + individual_X$S_hasanimals + individual_X$S_animalsinside + individual_X$S_garbage + individual_X$S_washhands)


  #clustered standard error 
  #value in the brackets 
  cl_se[i] <-coeftest(model1, vcov=vcovCL, cluster= individual_X$idcluster)[2,2]

  #coefficient for dpisofirme 
  coefs[i] <-  model1$coefficients[2]
  
  
}


coef_over_mean <- 100*(coefs / ctrl_grp_mean)


```

gl INmodel_3 $CH_demog dmiss_CH_demog* dtriage* $HH_health dmiss_HH_health* $HH_social dmiss_S_cash*;


HH_health S_waterland S_waterhouse S_electricity S_hasanimals S_animalsinside S_garbage S_washhands

HH_social  S_cashtransfers S_milkprogram S_foodprogram S_seguropopular;
### Model 3 
```{r}

coefs <- c()
cl_se <- c()

for(i in 1:5){
  #intercept 
  model1 <- lm(dependent_vars[,i] ~ individual_X$dpisofirme + 
                 individual_X$S_HHpeople + individual_X$S_rooms + 
                 individual_X$S_age + individual_X$S_gender + 
                 individual_X$S_childma + individual_X$S_childmaage + 
                 individual_X$S_childmaeduc + 
                 individual_X$S_childpa + individual_X$S_childpaage + 
                 individual_X$S_childpaeduc + individual_X$S_waterland + individual_X$S_waterhouse + individual_X$S_electricity + individual_X$S_hasanimals + individual_X$S_animalsinside + individual_X$S_garbage + individual_X$S_washhands + individual_X$S_cashtransfers + individual_X$S_milkprogram 
               + individual_X$S_foodprogram + individual_X$S_seguropopular)


  #clustered standard error 
  #value in the brackets 
  cl_se[i] <-coeftest(model1, vcov=vcovCL, cluster= individual_X$idcluster)[2,2]

  #coefficient for dpisofirme 
  coefs[i] <-  model1$coefficients[2]
  
  
}


coef_over_mean <- 100*(coefs / ctrl_grp_mean)


```
